SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2019-03-31 abs.tex
Rebuttal Changes

  In this paper, we introduce Perceptron-based Prefetch Filtering
  (PPF) as a way to increase the coverage of the prefetches generated by
  a baseline prefetcher without negatively impacting accuracy. PPF
  enables more aggressive tuning of a given baseline prefetcher,
  leading to increased coverage by filtering out the growing numbers
  of inaccurate prefetches such an aggressive tuning implies. We also
  explore a range of features to use to train PPF's perceptron layer
  to identify inaccurate prefetches. PPF improves performance on a
  memory-intensive subset of the SPEC CPU 2017 benchmarks by 3.78\%
  for a single-core configuration, and by 11.4\% for a 4-core
  configuration, compared to the baseline prefetcher alone.

>>>>

  In this paper, we introduce Perceptron-based Prefetch Filtering
  (PPF) as a way to increase the coverage of the prefetches generated by
  {\color{red}an underlying} prefetcher without negatively impacting accuracy. PPF
  enables more aggressive tuning of {\color{red}the underlying prefetcher},
  leading to increased coverage by filtering out the growing numbers
  of inaccurate prefetches such an aggressive tuning implies. We also
  explore a range of features to use to train PPF's perceptron layer
  to identify inaccurate prefetches. PPF improves performance on a
  memory-intensive subset of the SPEC CPU 2017 benchmarks by 3.78\%
  for a single-core configuration, and by 11.4\% for a 4-core
  configuration, compared to the \color{red}underlying prefetcher alone.

### 2019-03-31 back.tex
Rebuttal Changes

\subsection{Baseline Prefetcher: SPP}
\label{Background-SPP}

Kim {\em et. al.} proposed Signature Path Prefetcher (SPP)~\cite{SPP},
a confidence-based lookahead prefetcher.  SPP creates a signature
associated with a page address by compressing the history of
accesses. By correlating the signature with future likely delta
patterns, SPP learns both simple and complicated memory access
patterns quickly.  While the basic idea of perceptron based prefetch
filtering is applicable to any lookahead prefetcher, we develop a
practical implementation of our proposed perceptron prefetch filter
using SPP as our baseline.  Here we describe the basic architecture of
SPP.

>>>>

\subsection{{\color{red}Underlying Prefetcher: SPP}}
\label{Background-SPP}

Kim {\em et. al.} proposed Signature Path Prefetcher (SPP)~\cite{SPP},
a confidence-based lookahead prefetcher.  SPP creates a signature
associated with a page address by compressing the history of
accesses. By correlating the signature with future likely delta
patterns, SPP learns both simple and complicated memory access
patterns quickly.  While the basic idea of perceptron based prefetch
filtering is applicable to any lookahead prefetcher, we develop a
practical implementation of our proposed perceptron prefetch filter
using SPP as our {\color{red}underlying mechanism}. 
Here we describe the basic architecture of SPP.

### 2019-03-31 conc.tex
Rebuttal Changes

\section{Conclusion}
\label{Conclusion}
In this paper, we introduce the Perceptron-Based Prefetch Filtering
(PPF).  PPF acts as an independent check on the quality of predictions
made by the underlying prefetch engine.  We also created a case study
implementation of PPF using SPP as the baseline prefetch engine, while
in principle other prefetchers could be used.  We show that PPF
effectively filters bad prefetches, such that the given underlying
prefetcher can be highly aggressively tuned to achieve increasing
coverage.  PPF improves performance over the base prefetcher by up to
11.4\%.  PPF is a robust and adaptable technique that can be used to
enhance any existing prefetcher and can be a valuable tool in the
design of future memory latency constrained systems.

>>>>

\section{Conclusion}
\label{Conclusion}
In this paper, we introduce the Perceptron-Based Prefetch Filtering
(PPF).  PPF acts as an independent check on the quality of predictions
made by the underlying prefetch engine.  We also created a case study
implementation of PPF using SPP as the {\color{red}underlying prefetcher}, while
in principle other prefetchers could be used.  We show that PPF
effectively filters bad prefetches, such that the given underlying
prefetcher can be highly aggressively tuned to achieve increasing
coverage.  PPF improves performance over the {\color{red}underlying} 
prefetcher by up to 11.4\%.  PPF is a robust and adaptable technique 
that can be used to enhance any existing prefetcher and can be a 
valuable tool in the design of future memory latency constrained systems.

### 2019-03-31 design_arch.tex
Rebuttal Changes

Perceptron learning is a light-weight mechanism to pull together
disparate forms of information and synthesize a decision from
them. Our work considers a number of features corresponding to a
prefetch, such as speculation depth, page address and offset, and uses
this information as the inputs to our perceptron-based filter in order
to predict the usefulness of a prefetch.  Here, we discuss our the
design of our proposed perceptron prefetch filter (PPF).  PPF enhances
a base prefetcher by filtering out predicted unused prefetches. PPF is
a generalized prefetch filtering mechanism that may be adapted to any
prefetcher with appropriate feature selection and modifications which
we describe below.

@@

\noindent \textbf{Inferencing}\\
%ETG:is this like an explanation of how prefetching happens? 
%EB: I see this as a short context of the datapath leading to the perc filter.
The base prefetcher is triggered on every demand access to the L2
Cache, as seen in Figure~\ref{fig:PPF_Hierarchy}.  At this point, 
it has the opportunity to trigger a prefetch.
If it does so, it will also need to decide how many cache blocks to
prefetch.  These blocks can be either placed in the L2 or L3 cache
according to the confidence of the prefetching mechanism.  Once the
base prefetcher is triggered, the suggested prefetch candidates are
fed to the perceptron filter to determine the usefulness of these
prefetches. The filter ultimately decides whether to issue the
prefetch suggestions of the base prefetcher. As shown in step 1
of Figure~\ref{fig:PPF_Datapath}(a), to make the decision,
each feature corresponding to a suggested prefetch is used to index a
table and all the corresponding weights are summed. The sum denotes
the confidence value for the suggested prefetch, and is thresholded
against two different values: $\tau_{hi}$ and $\tau_{lo}$.

@@

\noindent \textbf{Recording}\\
As shown in step 2 of Figure~\ref{fig:PPF_Datapath}(a) the prefetches
that make it through the inference stage are recorded in the
``Prefetch Table''. The prefetch table is a 1,024-entry, direct mapped
structure that contains all metadata required to re-index the
perceptron entries for training.

@@

\noindent \textbf{Feedback and Data Retrieval}\\
As depicted in step 3, when there is an eviction or a demand access 
to the L2, training for
both the base prefetcher and our filter mechanism is triggered. The
address of the cache block that triggered training is used to index
both the Prefetch and Reject tables. 10 bits of the address are used
to index tables, and another 6 bits to perform tag matching. Once the
base prefetcher has suggested a prefetch request, the corresponding
features are used to index the tables of weights.

@@

Parallel to accessing the prefetch table, on a demand access, the
reject table is accessed. Before the demand access triggers the next
set of prefetches, the reject table is checked for a valid entry. A
hit means that the corresponding cache block was initially suggested
by the base prefetcher, but wrongly rejected by the perceptron
filter. The perceptron filter learns from this and makes use of the
corresponding features associated to the original prefetch request,
which are stored in the reject table, to index the weights tables and
adjust the weights accordingly.
The implementation of the reject table, allows us to capture the 
information of prefetches that were rejected, and that can be used 
to further optimize our prefetching mechanism.
%
%\pg{what prior work? this reference is too oblique to be useful,
%  either be specific or drop this paragraph} 
% Prior work in this domain
% lacks the knowledge of which cache blocks should have been prefetched,
% but were not.

@@

\subsection{Optimizing PPF for a Given Prefetcher}
\label{Arch-Generalizing}
The above discussion of PPF shows that it is highly modular and can be
adapted to be used over any base prefetcher for increased prefetch
accuracy. As a first step, all the prefetch
candidates of the prefetcher have to pass through the perceptron filter. 
If qualified, the metadata for perceptron indexing has to be stored. 
Next, when the feedback of a prior prefetch is available in form
of a subsequent demand hit or cache eviction, the stored
metadata needs to be retrieved to update the state of the perceptrons.
% \pg{this isn't quite right, I thought we were taking some metadata
%   from the prefetcher itself like confidence.  You should explicitly
%   mention that prefetcher metadata can be used, update the figure to
%   show that metadata passing from SPP to the prefetcher and point to
%   the figure to show where that connection is}

In general, PPF can be adapted to a new base prefetcher with only a
few modifications:

\noindent \textbf{Making Base Prefetcher More Aggressive:} By Tuning 
down any internal thresholds or throttling mechanisms to increase its
aggressiveness.

@@

\noindent \textbf{Feature Selection:} Perceptrons essentially
integrate contributions from different features to get a single sum
representing the final confidence.  Thus, perceptron learning can only
be as good as the set of features chosen.  Interestingly, this is what
makes perceptron learning scalable, as it can easily learn to
incorporate newer information in the form of new features.  Some of
the features we developed use information derived directly from
program execution, agnostic to the baseline prefetcher.  Beyond that,
the feature set can be expanded to convey any useful information or
metadata available in the baseline prefetcher.

\noindent \textbf{Using Metadata from the Prefetcher:} Some of the 
internal counters specific to the underlying prefetcher can be suitable candidates
for the perceptron features. To make sure that the perceptron layer sees that, 
the relevant meta-data must be exported from the prefetcher to PPF. This way,
PPF can be optimized to work tightly-knit with the base prefetcher.

>>>>

Perceptron learning is a light-weight mechanism to pull together
disparate forms of information and synthesize a decision from
them. Our work considers a number of features corresponding to a
prefetch, such as speculation depth, page address and offset, and uses
this information as the inputs to our perceptron-based filter in order
to predict the usefulness of a prefetch.  Here, we discuss our the
design of our proposed perceptron prefetch filter (PPF).  PPF enhances
{\color{red}an underlying prefetcher} by filtering out predicted unused prefetches. 
PPF is a generalized prefetch filtering mechanism that may be adapted 
to any prefetcher with appropriate feature selection and modifications 
which we describe below.

@@

\noindent \textbf{Inferencing}\\
%ETG:is this like an explanation of how prefetching happens? 
%EB: I see this as a short context of the datapath leading to the perc filter.
The {\color{red}prefetcher} is triggered on every demand access to the L2
Cache, as seen in Figure~\ref{fig:PPF_Hierarchy}.  At this point, 
it has the opportunity to trigger a prefetch.
If it does so, it will also need to decide how many cache blocks to
prefetch.  These blocks can be either placed in the L2 or L3 cache
according to the confidence of the prefetching mechanism.  Once the
{\color{red}underlying} prefetcher is triggered, the suggested prefetch candidates are
fed to the perceptron filter to determine the usefulness of these
prefetches. The filter ultimately decides whether to issue the
prefetch suggestions of the {\color{red}underlying} prefetcher. As shown in step 1
of Figure~\ref{fig:PPF_Datapath}(a), to make the decision,
each feature corresponding to a suggested prefetch is used to index a
table and all the corresponding weights are summed. The sum denotes
the confidence value for the suggested prefetch, and is thresholded
against two different values: $\tau_{hi}$ and $\tau_{lo}$.

@@

\noindent \textbf{Recording}\\
As shown in step 2 of Figure~\ref{fig:PPF_Datapath}(a) the prefetches
that make it through the inference stage are recorded in the
``Prefetch Table''. The prefetch table is a 1,024-entry, direct mapped
structure that contains all metadata required to re-index the
perceptron entries for training. {\color{red}10 bits of the address are used to index 
the tables, and another 6 bits to perform tag matching.}

@@

\noindent \textbf{Feedback and Data Retrieval}\\
As depicted in step 3, when there is an eviction or a demand access 
to the L2, training for both the {\color{red}underlying} prefetcher and our filter 
mechanism is triggered. The address of the cache block that triggered 
the training is used to index both the Prefetch and Reject tables. 
{\color{red}If it is a match, the corresponding
features are retrieved to index the tables of perceptron weights.}

@@

Parallel to accessing the prefetch table, on a demand access, the
reject table is accessed. Before the demand access triggers the next
set of prefetches, the reject table is checked for a valid entry. A
hit means that the corresponding cache block was initially suggested
by the {\color{red}underlying} prefetcher, but wrongly rejected by the perceptron
filter. The perceptron filter learns from this and makes use of the
corresponding features associated to the original prefetch request,
which are stored in the reject table, to index the weights tables and
adjust the weights accordingly.
The implementation of the reject table, allows us to capture the 
information of prefetches that were rejected, and that can be used 
to further optimize our prefetching mechanism.
%
%\pg{what prior work? this reference is too oblique to be useful,
%  either be specific or drop this paragraph} 
% Prior work in this domain
% lacks the knowledge of which cache blocks should have been prefetched,
% but were not.

@@

\subsection{Optimizing PPF for a Given Prefetcher}
\label{Arch-Generalizing}
The above discussion of PPF shows that it is highly modular and can be
adapted to be used over any {\color{red}underlying} prefetcher for increased prefetch
accuracy. As a first step, all the prefetch
candidates of the prefetcher have to pass through the perceptron filter. 
If qualified, the metadata for perceptron indexing has to be stored. 
Next, when the feedback of a prior prefetch is available in form
of a subsequent demand hit or cache eviction, the stored
metadata needs to be retrieved to update the state of the perceptrons.
% \pg{this isn't quite right, I thought we were taking some metadata
%   from the prefetcher itself like confidence.  You should explicitly
%   mention that prefetcher metadata can be used, update the figure to
%   show that metadata passing from SPP to the prefetcher and point to
%   the figure to show where that connection is}

In general, PPF can be adapted to a {\color{red}new prefetcher} with only a
few modifications:

\noindent \textbf{Making {\color{red}Underlying} Prefetcher More Aggressive:} By Tuning 
down any internal thresholds or throttling mechanisms to increase its
aggressiveness.

@@

\noindent \textbf{Feature Selection:} Perceptrons essentially
integrate contributions from different features to get a single sum
representing the final confidence.  Thus, perceptron learning can only
be as good as the set of features chosen.  Interestingly, this is what
makes perceptron learning scalable, as it can easily learn to
incorporate newer information in the form of new features.  Some of
the features we developed use information derived directly from
program execution, agnostic to the {\color{red}underlying} prefetcher.  Beyond that,
the feature set can be expanded to convey any useful information or
metadata available in the {\color{red}underlying} prefetcher.

\noindent \textbf{Using Metadata from the Prefetcher:} Some of the 
internal counters specific to the underlying prefetcher can be suitable candidates
for the perceptron features. To make sure that the perceptron layer sees that, 
the relevant meta-data must be exported from the prefetcher to PPF. This way,
PPF can be optimized to work tightly-knit with the {\color{red}underlying} prefetcher.

### 2019-03-31 design_impl.tex
Rebuttal Changes

\subsection{Features used by Perceptron}
\label{Impl-Features}
Here we discuss the various features that correlate the prefetching
decision with the program behavior.  All the features we used can be
derived from the information available in the L2 Cache access stream
or are taken as metadata derived from the baseline prefetcher.  Our
feature selection involved searching over a large space of relevant
perceptron features.  Note that part of the process of tuning PPF to a
specific prefetcher involves examining the available metadata in the
prefetcher itself, and thus PPF is attuned to the baseline
prefetcher's design. Using the statistical methodology outlined in
Section~\ref{Method-Features}, we pruned the feature set to a minimal
yet relevant set of features.
% \pg{again you want to get at why
% these were chosen. Also mention that you searched over a large
% space of possible features and these were the best.}
%
% [EB] Tried addressing. Does it look redundant when read after 'Feature Selection'
% bullet from the previous section?

>>>>

\subsection{Features used by Perceptron}
\label{Impl-Features}
Here we discuss the various features that correlate the prefetching
decision with the program behavior.  All the features we used can be
derived from the information available in the L2 Cache access stream
or are taken as metadata derived from the {\color{red}underlying} prefetcher.  Our
feature selection involved searching over a large space of relevant
perceptron features.  Note that part of the process of tuning PPF to a
specific prefetcher involves examining the available metadata in the
prefetcher itself, and thus PPF is attuned to the {\color{red}underlying}
prefetcher's design. Using the statistical methodology outlined in
Section~\ref{Method-Features}, we pruned the feature set to a minimal
yet relevant set of features.
% \pg{again you want to get at why
% these were chosen. Also mention that you searched over a large
% space of possible features and these were the best.}
%
% [EB] Tried addressing. Does it look redundant when read after 'Feature Selection'
% bullet from the previous section?

### 2019-03-31 intro.tex
Rebuttal Changes

Here, we propose Perceptron-based Prefetch Filtering (PPF) as an
enhancement to existing state-of-the-art prefetchers, allowing them to
speculate deeply to achieve high coverage while filtering out the
inaccurate prefetches this deep speculation implies.  PPF works by
observing the stream of candidate prefetches generated by a
prefetcher, and then rejects those that are predicted by the
online-trained neural model to be inaccurate.  The state-of-the-art
prefetcher that we use to evaluate PPF in this paper is the Signature
Path Prefetcher (SPP)~\cite{SPP}, however as we describe, PPF can be
designed to benefit any prefetcher.  In this design, PPF replaces
SPP's existing confidence-based throttling mechanism, which itself was
a highly tuned feature of that prefetcher.  Because PPF is so much
more effective at rejecting inaccurate prefetches than SPP's baseline
mechanism, we are free to re-tune the rest of SPP's design around
maximizing coverage. The result is an increase in both accuracy and
coverage, and a notable increase in performance.

>>>>

Here, we propose Perceptron-based Prefetch Filtering (PPF) as an
enhancement to existing state-of-the-art prefetchers, allowing them to
speculate deeply to achieve high coverage while filtering out the
inaccurate prefetches this deep speculation implies.  PPF works by
observing the stream of candidate prefetches generated by a
prefetcher, and then rejects those that are predicted by the
online-trained neural model to be inaccurate.  The state-of-the-art
prefetcher that we use to evaluate PPF in this paper is the Signature
Path Prefetcher (SPP)~\cite{SPP}, however as we describe, PPF can be
designed to benefit any prefetcher.  In this design, PPF replaces
SPP's existing confidence-based throttling mechanism, which itself was
a highly tuned feature of that prefetcher.  Because PPF is so much
more effective at rejecting inaccurate prefetches than SPP's 
{\color{red}internal} mechanism, we are free to re-tune the rest of 
SPP's design around maximizing coverage. The result is an increase 
in both accuracy and coverage, and a notable increase in performance.

### 2019-03-31 method.tex
FINAL(?)
Rebuttal Changes

We initially came up a set of 23 features.  By studying cross
correlation of each of these features against others in a 23$\times$23
matrix, we identified pairs of features with correlation factor > 0.9
in magnitude and eliminated redundant features, using guidance from
Global and per-trace Pearson's factor of those features.  By doing
this, we reduced the feature count to 9.  Thus, in the final
implementation of PPF, no two features have a high correlation between
them. This way we can be sure that each feature makes a contribution
that cannot be captured using other features.

@@

@@

In terms of computations, the perceptron mechanism only introduces an
extra adder tree. The hash perceptron mechanism makes sure than there
is no actual vector multiplication happening in the hardware.
Obtaining the perceptron sum requires addition of 9 5-bit numbers.
Using an adder tree of 4 5-bit adders, this can be done in
ceil($log_{2}9$) = 4 steps. Perceptron update only requires weight
update by +1 or -1. Thus, all the operations required for perceptron
inferencing or updating the states of the perceptrons can be easily
done in the time constraints of L2 Cache Accesses.

>>>>

We initially came up {\color{red}with} a set of 23 features.  By studying cross
correlation of each of these features against others in a 23$\times$23
matrix, we identified pairs of features with correlation factor > 0.9
in magnitude and eliminated redundant features, using guidance from
Global and per-trace Pearson's factor of those features.  By doing
this, we reduced the feature count to 9.  Thus, in the final
implementation of PPF, no two features have a high correlation between
them. This way we can be sure that each feature makes a contribution
that cannot be captured using other features.

@@

In terms of computations, the perceptron mechanism only introduces an
extra adder tree. The hash perceptron mechanism makes sure than there
is no actual vector multiplication happening in the hardware.
Obtaining the perceptron sum requires addition of {\color{red}nine} 
5-bit numbers.
Using an adder tree of {\color{red}four} 5-bit adders, this can be done in
ceil($log_{2}9$) = 4 steps. Perceptron update only requires weight
update by +1 or -1. Thus, all the operations required for perceptron
inferencing or updating the states of the perceptrons can be easily
done in the time constraints of L2 Cache Accesses.

@@

### 2019-03-31 related.tex
Rebuttal Changes

A low-accuracy aggressive prefetcher can significantly harm
performance.  To minimize interference from prefetching, Wu \textit{et
  al.} propose PACMan~\cite{pacman}, a prefetch-aware cache management
policy. PACMan dedicates some LLC sets to each of three competing
policies that treat demand and prefetch requests differently, using
the policy in the rest of the cache that shows the fewest
misses. Seshadri \textit{et al.} propose ICP~\cite{icp}, which demotes
a prefetch to the lowest reuse priority on a demand hit, based on the
observation that most prefetches are dead after their first hit. To
address prefetcher-caused cache pollution, it also uses a variation of
EAF~\cite{eaf} to track prefetching accuracy, and inserts only
accurate prefetches to the higher priority position in the LRU
stack. Jain \textit{et al.} propose Harmony~\cite{Harmony} to
accomodate prefetches in their MIN algorithm-inspired Hawkeye cache
management system.

@@

Peled \textit{et al.} introduce interesting ideas for on-line
Reinforcement Learning and dynamically scaling the magnitude of
feedback given to the baseline prefetcher~\cite{Semantics}. The
prefetcher relies on compiler support to receive features and build
the context.  Liao \textit{et al.}  focus on prefetching for data
center applications~\cite{Datacenter}.  They use offline machine
learning algorithms such as SVMs and logistic regression to do a
parametric search for an optimal prefetcher configuration.

>>>>

A low-accuracy aggressive prefetcher can significantly harm
performance.  To minimize interference from prefetching, Wu \textit{et
  al.} propose PACMan~\cite{pacman}, a prefetch-aware cache management
policy. PACMan dedicates some LLC sets to each of three competing
policies that treat demand and prefetch requests differently, using
the policy in the rest of the cache that shows the fewest
misses. Seshadri \textit{et al.} propose ICP~\cite{icp}, which demotes
a prefetch to the lowest reuse priority on a demand hit, based on the
observation that most prefetches are dead after their first hit. To
address prefetcher-caused cache pollution, it also uses a variation of
EAF~\cite{eaf} to track prefetching accuracy, and inserts only
accurate prefetches to the higher priority position in the LRU
stack. Jain \textit{et al.} propose Harmony~\cite{Harmony} to
accomodate prefetches in their MIN algorithm-inspired Hawkeye cache
management system. {\color{red}Ebrahimi \textit{et al} introduce
HPAC~\cite{HPAC} which provides a coordinated control between 
multiple prefetchers present in A CMP by looking at the 
prefetcher-induced inter-core interferance.}

@@

Peled \textit{et al.} introduce interesting ideas for on-line
Reinforcement Learning and dynamically scaling the magnitude of
feedback given to the baseline prefetcher~\cite{Semantics}. The
prefetcher relies on compiler support to receive features and build
the context.  Liao \textit{et al.}  focus on prefetching for data
center applications~\cite{Datacenter}.  They use offline machine
learning algorithms such as SVMs and logistic regression to do a
parametric search for an optimal prefetcher configuration. 
{\color{red}Hasheni \textit{et. al.}~\cite{LSTM} categorize prefetching as a 
regression problem and use LSTM based Deep Learning approach.}

### 2019-03-31 results.tex
Rebuttal Changes

% djimenez: is this geometric mean? if so, say so.
% [EB] Resolved
On the full SPEC CPU 2017 suite, PPF improves the geometric mean IPC
of the baseline by \textbf{15.24\%}, which is \textbf{2.27\%} better
than the next best prefetcher -- SPP.

@@

\noindent \textbf{8-Core:} The sorted comparison of speedups on the
memory intensive 8-core mixes is shown in
Figure~\ref{Fig:8Core_SPEC2017}.  PPF improves baseline performance by
\textbf{37.6\%}, an improvement of \textbf{9.65\%} over SPP. For a
random set of SPEC CPU 2017 mixes (not illustrated for space reasons),
PPF improves performance by \textbf{23.4\%} over the baseline,
corresponding to \textbf{4.6\%} over SPP. This increased improvement
achieved by PPF over the base engine SPP in a multi-core environment
is expected as PPF is a very accurate filter. Thus, it eliminates
useless prefetches before they can cause pollution in the shared LLC.
BOP offers a better improvement than SPP for the memory intensive
mixes. This superiority can be attributed to BOP's inherent aggressive
nature. DA-AMPM is also ahead of SPP in both the mixes. Interestingly,
in all these cases, PPF consistently outperforms the best performing
prefetcher.

>>>>

% djimenez: is this geometric mean? if so, say so.
% [EB] Resolved
On the full SPEC CPU 2017 suite, PPF improves the geometric mean IPC
of the baseline by \textbf{15.24\%}, which is \textbf{2.27\%} better
than the next best prefetcher -- SPP. {\color{red}For PPF, the average 
lookahead depth over the full benchmark is 3.97, while it is 3.28 for just 
SPP. It is evident that on average for SPP, our scheme allows the 
prefetcher to speculate 21\% deeper.}

@@

\noindent \textbf{8-Core:} The sorted comparison of speedups on the
memory intensive 8-core mixes is shown in
Figure~\ref{Fig:8Core_SPEC2017}.  PPF improves baseline performance by
\textbf{37.6\%}, an improvement of \textbf{9.65\%} over SPP. For a
random set of SPEC CPU 2017 mixes (not illustrated for space reasons),
PPF improves performance by \textbf{23.4\%} over the baseline,
corresponding to \textbf{4.6\%} over SPP. This increased improvement
achieved by PPF over the {\color{red}underlying prefetcher, SPP,} 
in a multi-core environment is expected as PPF is a very accurate filter. 
Thus, it eliminates useless prefetches before they can cause pollution in the 
shared LLC. BOP offers a better improvement than SPP for the memory intensive
mixes. This superiority can be attributed to BOP's inherent aggressive
nature. DA-AMPM is also ahead of SPP in both the mixes. Interestingly,
in all these cases, PPF consistently outperforms the best performing
prefetcher.
